 \documentclass[11pt]{article}

\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amscd}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{enumerate}

\newcommand{\ZZ}{\mathbb{Z}}

\setlength{\evensidemargin}{1in}
\addtolength{\evensidemargin}{-1in}
\setlength{\oddsidemargin}{1.5in}
\addtolength{\oddsidemargin}{-1.5in}
\setlength{\topmargin}{1in}
\addtolength{\topmargin}{-1.5in}

\setlength{\textwidth}{16cm}
\setlength{\textheight}{23cm}

\newcommand{\rook}{\hspace{-.1cm}\amalg\hspace{-.15cm}\bar{}}
\newcommand{\Stab}{\mathrm{Stab}}
\newcommand{\FF}{\mathbb{F}}


\begin{document}
\begin{center}
\section*{William Daniels}
\section*{CSCI 4202}
\subsection*{Artificial Intelligence}
\subsection*{Homework \#5 02/25/2015}
\end{center}

\vspace{.25cm}
\begin{enumerate}
\item First, we'll re-list the axioms from assignment 4 in clause form: \\\\
\begin{enumerate}[(a)]
\item $\neg food(x_1) \vee like(x_1, John)$
\item $food(Apples)$
\item $food(Chicken)$
\item $\neg eats(x_4, y_4) \vee killedBy(x_4, y_4) \vee food(x_4)$
\item $\neg eats(Peanuts, Bill) \vee \neg killedBy(peanuts, Bill)$
\item $\neg eats(x_6, Bill) \vee eats(x_6, Sue)$
\end{enumerate}
alright, excellent, now we're going to prove that John likes peanuts. So, first we negate our statement and put it into clause form (in that order!): $\neg like(Peanuts, John)$\\
Sweet, now using a subsitution we apply the resolution procedure as follows: 
$$\neg like(Peanuts, John)$$
\begin{align*}
&1 \rightarrow \text{ Replacement: } \left ( \frac{Peanuts}{x_1} \right ) \neg food(Peanuts)\\
&4 \rightarrow \text{ Replacement: } \left ( \frac{Peanuts}{x_4}, \frac{Bill}{y_4} \right )  \neg eats(Peanuts, Bill) \vee killedBy(Peanuts, Bill)\\
&5 \rightarrow   \neg eats(Peanuts, Bill) \vee \neg eats(Peanuts, Bill)\\
\end{align*}
this is true and true, therefore, our clause is false, John does not like peanuts. 
\item First, we represent the facts in predicate logic: 
\begin{enumerate}[(1)]
\item $ClubMember(Joe)$
\item $ClubMember(Sally)$
\item $ClubMember(Ellen)$
\item $ClubMember(Bill)$
\item $Married(Joe, Sally)$
\item $Siblings(Bill, Ellen)$
\item $\forall x, \forall y: ClubMember(x) \wedge married(x, y) \rightarrow ClubMember(y)$
\item $LastMeetingAtHouseOf(Joe)$ 
\end{enumerate}
 Now, for part (b) we need to turn this into clause form, which is thankfully very simple: \\
\begin{enumerate}[(1)]
\item $ClubMember(Joe)$
\item $ClubMember(Sally)$
\item $ClubMember(Ellen)$
\item $ClubMember(Bill)$
\item $Married(Joe, Sally)$
\item $Siblings(Bill, Ellen)$
\item $\neg  ClubMember(x_7) \vee \neg married(x_7, y_7) \vee ClubMember(y_7)$
\item $LastMeetingAtHouseOf(Joe)$ 
\end{enumerate}
easy enough, Now. we need to try and decide the truth of the requested information, first: 
$LastMeetingAtHouseOf(Sally)$
Now, we negate it, and begin our resolution procedure: 
$$ \neg LastMeetingAtHouseOf(Sally)$$
\begin{align*}
&8 \rightarrow \text{ Replacement: } \left ( \frac{Joe}{Sally} \right ) Nothing else to do, we are finished. \qed\\
\end{align*}
now for, Ellen not being married. This one we cannot do, since the clause: $\neg married(Ellen, y)$ there is no associated item which which to pair it, therefore we must add some facts to the database. 
we add: 
\begin{enumerate}[(9)]
\item $\forall x \forall y : siblings(x, y) \rightarrow \neg married(x, y)$
\end{enumerate}
then into clause form: $\neg siblings(x_9, y_9) \vee married(x_9, y_9)$
From there it becomes simple, the derivation looks like the following: 
\begin{align*}
&\neg married(Ellen, x)\\
& 9 \rightarrow \text{ Replacement: } \left ( \frac{x}{y_9} \right ) Siblings(Ellen, x)\\
&6 \rightarrow \text{ Replacement: } \left ( \frac{Bill}{y_9} \right )\\
& \text{ Nothing else to do, we are finished. Ellen and Bill would not be siblings in this case, contradiction. } \qed\\
\end{align*}

\end{enumerate}







\end{document}

